Towards the end of the project we decided to implement a python module to do testing and analysis on some candidate probability distributions.
\section{Analysis design and goals}
    To visualize and motivate the scope of this analysis we expand Eq. \ref{eq:bounds} as follow
    \begin{equation}
    	\keyrate{X}{Y}{Z} \leq \redintrinfo{X}{Y}{Z} \leq \intrinfo{X}{Y}{Z} \leq I_{form} (X;Y|Z)
    \end{equation}
    including also the information of formation.\\
    It is tricky to get direct values for the secret key rate and information of formation --- the fundamental quantities for key agreement --- since they are defined over a \textit{possible protocol}. 
    For their bounds --- i.e. the central parts of the inequality --- we can obtain direct numerical values. \\
    The aim of this part of the project is then to take the candidate given in Fig. \ref{Tab:candidate2} and map the values of the reduced and normal intrinsic information for various variation of said probability distribution.\\
    
    A good result we hope to obtain is a probability distribution for which the reduced measures tend to $0$, while the intrinsic information remains larger than $0$. This will lead to a new candidate for bound information.\\
    
    In order to perform analysis on those measures we firstly had to implement a library of modules that dealt with the probability and information theory aspects.
    Following criteria for separability of quantum states, a quantum mechanics module was also implemented to translate and later tests the distributions from the quantum to classical regime.\\
    The intrinsic information (and the reduced counterpart) is defined as an \emph{infimum}. 
    To find a correct value it will be required to solve an optimization problem. 
    The definition given in section \ref{intrininfo} however does not allow us to formulate the problem as convex.
    We decided then to adopt a Monte-Carlo method find them.\\
     
    For each step --- i.e. for each variation --- of the candidate base probability, the values of 
    \begin{itemize}
    	\item	mutual information
    	\item	intrinsic information
    	\item	reduced intrinsic information
    	\item	trace over quantum state witness given in \cite{DPS04}
    \end{itemize}
    are measured.
\section{Different noises analysis}
    % results
\section{Scaling up dimensions}
    % results