Throughout the project, topics of information theory and quantum mechanics were researched thoroughly.
We have built an understanding why some aspects of quantum mechanics present an analog in classical key agreement and how they can be used as an intuition in research.
Moreover, we have seen how and why the question of bound information remains yet an open question.
We researched and understood the measures presented as bounds to define the amount of secrecy a probability distribution among parties can hold, and how much does it cost to build it.
Lastly, the implementation of a python library to perform a  numerical analysis of candidates was instrumental to observe how the measure of reduced intrinsic information is not a useful measure for the search of bound information.\\

As future work on the topic, more thought can be put into the usefulness of the reduced intrinsic information measure.
The intuitions on the bounds on $\Ent(U)$ and the minimization of the term $\intrinfo{X}{Y}{ZU}$ have to be formally stated.
The code produced during the project, while providing as a library of functions for the study, was not completed to the intended form, as it only tested the marginal of \ref{Tab:candidate} and not the tripartite distribution \ref{Tab:candidate2}.
More development can be done in the library to be able to test other candidate tripartite distributions.
More tests for separability criteria of the translated quantum states are already being added as a continuation of the work.