% Set title page for separate titlepage
\documentclass[titlepage]{report}

%---------% Packages %---------%
% Some standard math packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{IEEEtrantools}

% Package for lists
\usepackage[shortlabels]{enumitem}

% Graphics
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{tikz}
\usetikzlibrary{fit,
						backgrounds,
						arrows,
						decorations.markings,
						decorations.pathmorphing,
						snakes,
						shapes.misc, 
						positioning,
						scopes,
						calc}

\tikzset{colorbox/.style={thick, rounded corners=2pt, text height=1.7ex,text depth=.25ex, draw=#1!70!black, fill=#1!30}}

\tikzset{colorelement/.style={thick, rounded corners=2pt, draw=#1!70!black, fill=#1!30}}
\tikzset{conn/.style={thick, shorten <=#1, shorten >=#1}}
\tikzset{arr_node/.style={pos=0.5,above,font=\scriptsize, sloped}}

\usepackage{float}
\usepackage{multirow}
%\usepackage{gnuplot-lua-tikz}

% Utilities
\usepackage{lipsum}
\usepackage{arydshln}

% Biblatex
\usepackage[backend=biber,style=numeric,sorting=nty]{biblatex}
\nocite{*}
\addbibresource{bib/references.bib}

% Appendices
\usepackage[toc]{appendix}
%------------------------------------%

% Math environments
\theoremstyle{remark}
\newtheorem{remark}{Remark}
\newtheorem{xmpl}{Example}
\newtheorem{definition}{\textbf{Definition}}

%quantum commands
\renewcommand{\H}{\mathcal{H}}
\newcommand{\ket}[1]{|#1 \rangle}
\newcommand{\bra}[1]{\langle #1|}
\newcommand{\braket}[2]{\langle#1|#2\rangle}
\newcommand{\bk}[2]{\langle#1|#2\rangle}
\newcommand{\ketbra}[2]{|#1 \rangle\langle #2|}
\newcommand{\kb}[2]{|#1 \rangle\langle #2|}
\newcommand{\proj}[1]{|#1\rangle\langle #1|}

%Math commands
\DeclareMathOperator{\Tr}{Tr} % Trace
\DeclareMathOperator{\Ent}{H} % Entropy
\DeclareMathOperator{\I}{I} % Mutual Information
\newcommand{\keyrate}[3]{S(#1;#2||#3)} % secret key rate
\newcommand{\intrinfo}[3]{\I(#1;#2\!\downarrow\!#3)} % intrinsic information
\newcommand{\redintrinfo}[3]{\I(#1;#2\!\downdownarrows\!#3)} %reduced intrinsic information

%------------------------------------%

\begin{document}

\input{chapters/title}

\chapter*{Abstract}
%\begin{abstract}
There is a correspondence between entanglement distillation in quantum mechanics and classical key agreement in information theory. 
In the quantum-mechanical framework there are, furthermore, non-distillable, but entangled quantum states --- that is, states sharing bound entanglement. 
So, considering the above analogy, does there exists some notion of bound information? As of today this remains an open question.
In this project we follow the intuition from bound entanglement, the related measures and their connections to concepts of classical key agreement, as well as related information-theoretical concepts, in order to further investigate this open question.
We also look at a candidate probability distribution for bound information and perform numerical simulations in search for new, possibly better, candidates for bound information.\\

The structure of the report is as follows: 
after an explanation of the motivation of the search, chapter \ref{ch:two} explains the basics of key exchange in both classical and quantum mechanical frameworks.
 A comparison between methods is presented. 
 Chapters \ref{ch:three} and \ref{ch:four} give the foundations for information theoretical concepts needed to understand and work with theoretical security. 
 Chapter \ref{ch:five} summarizes the state of research on bound information and finally chapter \ref{ch:six} presents the numerical analysis conducted on probability distributions.
%\end{abstract}

%\chapter*{Acknowledgements}
%\lipsum[13]

\tableofcontents

%\chapter{Introduction}
%\input{chapters/Introduction}

\chapter{Motivation}
\input{chapters/Motivation}
		
% done
 \chapter{A Common Key Exchange Problem}
 \input{chapters/chapter2}
% done
\chapter{Information Theoretical Model of Cryptography: Random Variables}
\input{chapters/chapter3}
% done
\chapter{Measures of Correlation and Their Bounds}
\input{chapters/chapter4}
% done
 \chapter{State of Research}
 \input{chapters/chapter5}
% done
 \chapter{A Numerical Analysis of Candidate Distributions}
 \input{chapters/chapter6}
% empty
% \chapter{Conclusion}
% \input{chapters/Conclusion}

\begin{appendices}
	\chapter{Mathematical Framework for QM}
	\input{chapters/appendixA}
	\chapter{Quantum Mechanics}
	\input{chapters/appendixB}
%	\chapter{Information Theory}
%	\input{chapters/appendixC}
\end{appendices}

%\bibliographystyle{apalike}
\printbibliography
\end{document}
